QPLIB: A Library of Quadratic Programming Instances

### 2017-01-30 QPLIB-1.0.tex
minor revision on hans paragraph
- add references to solvers subsection and minlplib 2 citation
- the scripts were taken from scip, not miplib

While no performance issues of solvers for QP/QCP problems are considered in 
this paper, we refer to the comprehensive benchmark site \url{http://plato.asu.edu/bench.html}. Of the benchmarks
on this site three deal exlusively with QP/QCP problems: 
the (1) Large SOCP, (2) MISOCP, and the (3) MIQ(C)P benchmarks. 
The following contain partly results for such problems: 
(4) Parallel Barrier Solvers on Large LP/QP problems, (5) AMPL-NLP, (6) MINLP.
The benchmarks (1,2,4) have only convex instances, while the others include 
nonconvex instances. Global optima are obtained by several of the solvers in
the benchmarks (3,5).
All solvers in the latest addition (6) compute global optima, they are ANTIGONE,
BARON, COUENNE, LINDO, and SCIP. This benchmark is based on MINLPLIB2 \url{http://www.gamsworld.org/minlp/minlplib2/html/}, a
collection of presently 1388 instances. In order to give a first representative
impression of solver performance, care was taken to reduce the number and 
allow all solvers to finish in reasonable time. More than half of the selected
instances are QP or QCP. A time limit of two hours on a
modern workstation with sufficent memory was used. Computations were done in
GAMS with scripts derived from the MIPLIB scripts and available at Github.
For details we refer to \url{http://plato.asu.edu/ftp/minlp.html}.

>>>>

While no performance issues of solvers for QP/QCP problems are considered in 
this paper, we refer to the comprehensive benchmark site \url{http://plato.asu.edu/bench.html}. Of the benchmarks
on this site three deal exlusively with QP/QCP problems: 
the (1) Large SOCP, (2) MISOCP, and the (3) MIQ(C)P benchmarks. 
The following contain partly results for such problems: 
(4) Parallel Barrier Solvers on Large LP/QP problems, (5) AMPL-NLP, (6) MINLP.
The benchmarks (1,2,4) have only convex instances, while the others include 
nonconvex instances. Global optima are obtained by several of the solvers in
the benchmarks (3,5).
All solvers in the latest addition (6) compute global optima, they are ANTIGONE,
BARON, COUENNE, LINDO, and SCIP, c.f.~\S~\ref{subsec:solver}. This benchmark is based on MINLPLib~2 \cite{Vigerske2014}, a
collection of presently 1388 instances. In order to give a first representative
impression of solver performance, care was taken to reduce the number of instances and 
allow all solvers to finish in reasonable time. More than half of the selected
instances are QP or QCP. A time limit of two hours on a
modern workstation with sufficient memory was used. Computations were done in
GAMS with scripts derived from the SCIP check scripts and available at GitHub.
For details we refer to \url{http://plato.asu.edu/ftp/minlp.html}.
